---
title: "Principles of Accessible Data Visualization"
output: html_document
---

# Quizzes

## Quiz 1: Color Accessibility

1. Why is it important to avoid red/green reliance in data visualizations?
   - A. It is more visually appealing
   - B. To accommodate color blindness
   - C. It is a trendy design choice
   - D. To save printing costs

2. What can be used in addition to color to differentiate elements in a visualization?
   - A. Fonts and text size
   - B. Patterns, textures, or shapes
   - C. Sounds
   - D. Animation effects

## Quiz 2: User-Centered Approach

1. Why should you conduct research about your audience before creating a visualization?
   - A. To make the visualization look professional
   - B. To understand their needs and abilities
   - C. To decide on the color scheme
   - D. To impress stakeholders

2. What is the purpose of usability testing?
   - A. To test the performance of the software
   - B. To gather feedback from people with disabilities
   - C. To find bugs in the code
   - D. To finalize the design without user input

## Quiz 3: Visual Clarity and Simplicity

1. How should you declutter your design?
   - A. Use bright colors
   - B. Prioritize key information
   - C. Add more charts
   - D. Increase font size

2. What should you consider when choosing the right chart type?
   - A. The data and audience understanding
   - B. The colors available
   - C. The amount of text
   - D. The latest design trends

## Quiz 4: Beyond Vision

1. What is the purpose of audio descriptions in data visualization?
   - A. To provide a soundtrack
   - B. To explain the data for visually impaired users
   - C. To add more detail to the visualization
   - D. To make the visualization more engaging

2. Why is screen reader compatibility important?
   - A. To enhance visual appeal
   - B. To ensure text elements are accessible to screen readers
   - C. To improve performance
   - D. To follow design trends

## Quiz 5: Cultural Sensitivity and Collaboration

1. Why should cultural symbols and representations be considered in data visualizations?
   - A. To make the visualization colorful
   - B. To avoid stereotypes and biases
   - C. To include as many symbols as possible
   - D. To save space

2. How can you promote standards and policies for accessibility in data visualization?
   - A. By designing in isolation
   - B. By advocating for change
   - C. By avoiding feedback
   - D. By focusing on aesthetics only
   
## Answers
Quiz 1: Color Accessibility

1. Why is it important to avoid red/green reliance in data visualizations?
   - **B. To accommodate color blindness**

2. What can be used in addition to color to differentiate elements in a visualization?
   - **B. Patterns, textures, or shapes**

Quiz 2: User-Centered Approach

1. Why should you conduct research about your audience before creating a visualization?
   - **B. To understand their needs and abilities**

2. What is the purpose of usability testing?
   - **B. To gather feedback from people with disabilities**

Quiz 3: Visual Clarity and Simplicity

1. How should you declutter your design?
   - **B. Prioritize key information**

2. What should you consider when choosing the right chart type?
   - **A. The data and audience understanding**

Quiz 4: Beyond Vision

1. What is the purpose of audio descriptions in data visualization?
   - **B. To explain the data for visually impaired users**

2. Why is screen reader compatibility important?
   - **B. To ensure text elements are accessible to screen readers**

Quiz 5: Cultural Sensitivity and Collaboration

1. Why should cultural symbols and representations be considered in data visualizations?
   - **B. To avoid stereotypes and biases**

2. How can you promote standards and policies for accessibility in data visualization?
   - **B. By advocating for change**

# R Code Examples
## High Contrast and Color Accessibility
```{r}
# Load necessary library
library(ggplot2)

# Sample data
data <- data.frame(
  category = c("A", "B", "C", "D"),
  values = c(3, 12, 5, 18)
)

# Bar plot with high contrast colors
ggplot(data, aes(x = category, y = values, fill = category)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("A" = "#1b9e77", "B" = "#d95f02", "C" = "#7570b3", "D" = "#e7298a")) +
  theme_minimal() +
  theme(text = element_text(size = 14)) +  # Readable fonts
  labs(title = "High Contrast Bar Plot",
       x = "Category",
       y = "Values",
       fill = "Category") +
  theme(legend.position = "none")
```


## Clear Labeling and Choosing the Right Chart Type

```{r}
# Sample data
data2 <- data.frame(
  category = c("A", "B", "C", "D"),
  values = c(3, 12, 5, 18)
)

# Pie chart
ggplot(data2, aes(x = "", y = values, fill = category)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  scale_fill_manual(values = c("A" = "#1b9e77", "B" = "#d95f02", "C" = "#7570b3", "D" = "#e7298a")) +
  theme_void() +
  theme(text = element_text(size = 14)) +  # Readable fonts
  labs(title = "Pie Chart with Clear Labels",
       fill = "Category")
```


## Patterns, Textures, or Shapes for Differentiation
```{r}
# Load necessary libraries
library(ggplot2)
library(ggpattern)

# Sample data
data3 <- data.frame(
  category = c("A", "B", "C", "D"),
  values = c(3, 12, 5, 18)
)

# Bar plot with patterns
ggplot(data3, aes(x = category, y = values, pattern = category)) +
  geom_bar_pattern(stat = "identity", fill = "white", 
                   pattern_fill = c("#1b9e77", "#d95f02", "#7570b3", "#e7298a"), 
                   pattern_density = 0.1, pattern_angle = 45, 
                   pattern_spacing = 0.02) +
  theme_minimal() +
  theme(text = element_text(size = 14)) +  # Readable fonts
  labs(title = "Bar Plot with Patterns",
       x = "Category",
       y = "Values",
       pattern = "Category") +
  theme(legend.position = "none")
```




